2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Starting draft approach

---
title: "2019 Draft Prep"
author: "Tom Kain"
date: "March 19, 2019"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

@@

CF <- batters_ranked %>%
  filter(LF) %>%
  mutate(position = "CF")

@@

keepers <- c(
  "Justin turner",
  "Miles Mikolas",
  "Whit Merrifield",
  "Archie Bradley",
  "Patrick Corbin",
  "Matt Carpenter",
  "Blake Treinen",
  "Ronald Acuna Jr.",
  "Blake Snell",
  "Lorenzo Cain",
  "Trevor Story",
  "Andrew Benintendi",
  "Mike Clevinger"
)

@@

positions_ranked_with_keepers %>%
  filter(ADP <= 300,
         !keeper) %>%
  ggplot(aes(x=position, y=z_sum)) +
  geom_boxplot() +
  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
  labs(x="Position",
       y="Z_Points",
       title="Player value by position, top 300 drafted") -> ptk

@@

>>>>

---
title: "2019 Draft Prep"
author: "Tom Kain"
date: "March 19, 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

@@

CF <- batters_ranked %>%
  filter(CF) %>%
  mutate(position = "CF")

@@

keepers <- c(
  "Justin Turner",
  "Miles Mikolas",
  "Whit Merrifield",
  "Archie Bradley",
  "Patrick Corbin",
  "Matt Carpenter",
  "Blake Treinen",
  "Ronald Acuna Jr.",
  "Blake Snell",
  "Lorenzo Cain",
  "Trevor Story",
  "Andrew Benintendi",
  "Mike Clevinger"
)

@@

positions_ranked_with_keepers %>%
  filter(ADP <= 300,
         !keeper) %>%
  ggplot(aes(x=position, y=z_sum)) +
  geom_boxplot() +
  geom_jitter(aes(text=Name, alpha=desc(round)), width = .2) +
  geom_abline(slope=0, intercept = 0, linetype = "dotted") +
  labs(x="Position",
       y="Z_Points",
       title="Player value by position, top 300 drafted, keepers excluded ") -> ptk

@@

*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*

I'd like to put together a plan of attack where, for each round, I identify the kinds of players available at the highest projected scoring, perhaps in tiers of z_scores: >= 15, 10-15, 5-10, etc. Let's start with the upper tier:

##### Elite Tier (z_score >= 15)

```{r echo = FALSE}
positions_ranked_with_keepers %>%
  filter(z_sum >= 15) %>%
  select(Name, z_sum, ADP, round) %>%
  unique() %>%
  arrange(ADP) %>%
  kable()
```

We should assume Trout, Betts, and Ramirez will go 1,2,3, or at least not make it to me at 11. However, according to the projection data, Bryce Harper & Juan Soto could be available, potentially worth getting at the rounds 1 & 2 turn.
